Sensitivity to measurement error in dissolved gas measurements

### 2024-06-18 scripts/DG_sensitivity_to_measurement_error.Rmd
Added mixing scenarios. Added .md file to repo

```{r setup, warning=FALSE, message=FALSE}
library(knitr)
library(rmarkdown)
library(bayesplot)
library(kableExtra)
library(ggpubr)
library(tidyverse)
library(tidybayes)
library(ggplot2)
library(ggExtra)
library(gridExtra)
library(readxl)
library(janitor)
library(sf)

@@

-   $C$ = concentration (nM)
-   $B$ = barometric pressure (kPa)
-   $V_g$ = volume of reference gas in headspace (mL)
-   $M_h$ = gas mixture ratio in the headspace (C_e below)
-   $M_r$ = gas mixture ratio in the reference (C_a_n2o below)
-   $V_w$ = volume of water below the headspace (mL)
-   $K$ = temperature (K) (temp celsius or T_c + 273 below)
-   $H^{\theta}$ = Henry's law constant ($H_{N_2O}$ or $H_{Ar}$ below)

@@

-   $V$ = Total volume of the mixing vessel (e.g. 140mL syringe)
-   $V_g$ = Volume of gas (mL) in the mixing vessel 
-   $V_w$ = Volume of water (mL) in the mixing vessel
-   $R_M$ = Mixing ratio (gas:water)

## Simulate $\text{N}_2\text{O}$

```{r summary_empirical, echo=TRUE}
load(paste0(localPath, "\\Environmental Protection Agency (EPA)",
            "\\ORD NLA17 Dissolved Gas - Documents\\",
            "inputData\\dg.2021-02-01.RData"))

@@

Simulate a single concentration without measurment error to represent the "true" 
or "known" value for dissolved $\text{N}_2\text{O}$.
```{r dg_calc, echo=TRUE}
# Set volume of syringe/vessel
V <- 140 # 140mL syringe

@@

B <- 99 # barometric pressure (kPa)
V_g <- V * R_M # volume of reference gas in headspace
V_w <- V * (1 - R_M) # volume of water below headspace
T_c <- 23 # temperature ( C )
M_h <- 0.307 # gas mixture ratio in headspace (Mr_h) * Changes as function of R_M at constant C
M_a_n2o <- 0.310 # gas mixture ratio in reference (Mr_r)
H_n2o <- 0.00024 #mol m-3 Pa, range: 0.00018 - 0.00025; Henry's law constant
H_ar <- 0.000014 #mol m-3 Pa, range: 0.000013 - 0.000016; Henry's law constant

C <- 1e-6 * B * ( V_g * ( M_h - M_a_n2o ) / ( 8.3144598 * ( T_c + 273.15 ) * V_w ) + H_n2o * exp( 2700 * ( 1 / ( T_c + 273.15 ) - 1 / 298.15 ) ) * M_h )

@@

round( C, 1 ) 
```

```{r dg_calc_vary_r, echo=TRUE}
# Set volume of syringe/vessel
V <- 140 # 140mL syringe

B <- 99 # barometric pressure (kPa)
V_g <- V * R_M # volume of reference gas in headspace
V_w <- V * (1 - R_M) # volume of water below headspace
T_c <- 23 # temperature ( C )
M_h <- 0.307 # gas mixture ratio in headspace (Mr_h)
M_a_n2o <- 0.310 # gas mixture ratio in reference (Mr_r)
H_n2o <- 0.00024 #mol m-3 Pa, range: 0.00018 - 0.00025; Henry's law constant
H_ar <- 0.000014 #mol m-3 Pa, range: 0.000013 - 0.000016; Henry's law constant

C <- 1e-6 * B * ( V_g * ( M_h - M_a_n2o ) / ( 8.3144598 * ( T_c + 273.15 ) * V_w ) + H_n2o * exp( 2700 * ( 1 / ( T_c + 273.15 ) - 1 / 298.15 ) ) * M_h )

round( C, 1 ) 
```

## Empricial variation
Estimate variation due to measurement uncertainty using empirical data from
laboratory replicates.
```{r get_gc_error, echo=FALSE}
# READ GC DATA----------------
##########################################################################
#       Code is commented out because collaborators may not have access  #
#       to the file paths. The calculated standard deviation is hard     #
#       coded below.
##########################################################################

@@

Measurement error is defined here as the standard deviation of repeated
analysis of analytical standards throughout the period of time that the
NLA2017 samples were analyzed, which was $\sigma$ = `r n2o_sd_epa`.

## Simulate measurment error

Below, potential errors associated with dissolved $\text{N}_2\text{O}$ 
measurement are simulated and assessed separately for GC observations in:

@@

Measurement error is then simulated and assessed separately for:

@@

    (5) water volume

Finally, all of the sources (1, 2, 4, 5, and 6) are simulated
simultaneously and assessed as the total variation in dissolved
$\text{N}_2\text{O}$. This total error is then added to the point estimates for 
$\text{N}_2\text{O}$ observed in this study, which results in an estimate of
uncertainty due to measurement error. These error from these simulations was also
carried through to estimated of the saturation ratio. The source-sink status for
each site included in this study was then mapped to present a source-sink 
categorization that reflected these estimated uncertainties. The categorization 
was made such that any observation with simulated error that was within the 
central 95th percentile of

Set the number of simulations for error:

```{r set_n_sims}
nsim <- 1e5
```

### Equilibrated headspace
Simulate measurment error in dissolved $\text{N}_2\text{O}$ due solely to variation in 
measurements within the equlibrated headspace.
```{r simulate_C_h_me, echo=TRUE, message=FALSE}
# Create empty vector to fill below with simulated values for N2O observed with 
# error due to variation in the GC measurments of gas in the equilibrated 
# headspace. The subscript, "me", denotes an observed or measured value, which 
# is contrasted with the known value, C, set above.
C_h_me <- rep(NA, nsim)

# The true value for the concentration of equilibrated gas in the headspace, 
# C_e, was set above. This step simulates additive error in this measurement 
# that is centered over the true value. The observed concentration of
# equilibrated gas is simulated as normally distributed variable, with a mean
# C_e, and a standard deviation specified as the observed sd of replicate GC 
# measurements in our lab. 
M_h_me <- rnorm(nsim, M_h, n2o_sd_epa)

@@

The results of the simulations are summarized with density histograms
below.

```{r plot_C_h_me, echo=FALSE, fig.align='center', fig.asp=0.35, fig.width=8}
ggarrange(
ggplot(C_h_df, aes(x = M_h_me, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.001) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = M_h , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("Simulated variation in \nequilibrated headspace (Mh) \nGC measurements") +
  xlab("Concentration (nmol L-1)"),

@@

ggplot(C_h_df, aes(x = C_h_me_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle("Absolute error in dissolved \nN2O estimate (observed - true) \n") +
  xlab("Error (nMol)"),
nrow = 1
)
```

### Ambient air
Error in the GC measurements of $\text{N}_2\text{O}$ in the ambient air ($M_a$) is simulated 
below. The result of the simulation is plotted as a histogram to illustrate the
variation in the measurement. THe resulting effect on the uncertainty of the 
dissolved N2O measurement is also plotted along with the absolute error in 
N2O as a result of error in this measurement.
```{r simulate_me_Ca, message=F}
C_a_me <- rep(NA, nsim)

M_a_n2o_me <- rnorm(nsim, M_a_n2o, n2o_sd_epa) # m.e. in measured gas in air

@@

ggplot(C_a_df, aes(x = C_a_me_abs, y = after_stat(density))) +  
  geom_histogram( binwidth = 0.01 ) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline( xintercept = 0 , color = 'red' ) +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle( "Absolute error in dissolved \nN2O estimate (observed - true) \n") +
  xlab( "Error (nMol)"),
nrow = 1)
```

### Water temperature

```{r simulate_me_T_c, message=F}
C_tc_me <- rep(NA, nsim)

@@

ggplot(C_tc_df, aes(x = C_tc_me_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.001) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) + 
  ggtitle("Absolute error in dissolved \nN2O estimate (observed - true) \n") +
  xlab("Error (nMol)"),
nrow = 1)
```

### Barometric pressure

```{r simulate_me_B, message=F}
C_b_me <- rep(NA, nsim)

@@

ggplot(C_b_df, aes(x = C_b_me_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.0001) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) + 
  ggtitle("Absolute error in dissolved \nN2O estimate (observed - true) \n") +
  xlab("Error (nMol)"),
nrow = 1)
```

### Water volume

```{r simulate_me_V_w, message=F}
C_w_me <- rep(NA, nsim)

@@

ggplot(C_w_df, aes(x = C_w_me_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.00025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) + 
  ggtitle("Absolute error in dissolved \nN2O estimate (observed - true) \n") +
  xlab("Error (nMol)"),
nrow = 1)
```

### All observables
Simulate measurement error for all observables (_i.e._, Equilibrated headspace, 
air, water temperature, and barometric pressure ) and the resulting effects on
dissolved N2O observations
```{r simulate_me_all, message=F}
C_all_me <- rep(NA, nsim)

>>>>

```{r setup, warning=FALSE, message=FALSE}
#library(devtools) # needed to install USAboundaries package from
library(knitr)
library(rmarkdown)
library(bayesplot)
library(kableExtra)
library(ggpubr)
library(tidyverse)
library(tidybayes)
library(ggplot2)
library(ggExtra)
library(gridExtra)
library(readxl)
library(janitor)
library(sf)

# Install USAboundaries package from GitHub
#devtools::install_github("ropensci/USAboundaries")

@@

-   $C$ = concentration (nM) dissolved in water
-   $B$ = barometric pressure (kPa)
-   $V_g$ = volume of reference gas in headspace (mL)
-   $M_h$ = gas measured in the equilibrated headspace
-   $M_r$ = gas measured in the reference
-   $V_w$ = volume of water below the headspace (mL)
-   $K$ = temperature (K) (T_c + 273 below)
-   $H^{\theta}$ = Henry's law constant ($H_{N_2O}$ or $H_{Ar}$ below)

@@

-   $V$ = Total volume of the mixing vessel (e.g. 140mL syringe)
-   $R_M$ = Gas mixing proportion (gas volume / mixing vessel volume)
-   $V_g$ = Volume of gas (mL) in the mixing vessel 
-   $V_w$ = Volume of water (mL) in the mixing vessel

## Calculate $\text{N}_2\text{O}$
Below is a summary of the empirical measurements of N2O (ppm) in the
equilibrated headspace.
```{r summary_empirical, echo=TRUE}
load(paste0(localPath, "\\Environmental Protection Agency (EPA)",
            "\\ORD NLA17 Dissolved Gas - Documents\\",
            "inputData\\dg.2021-02-01.RData"))

@@

Calculate a single concentration without measurement error to represent a 
"true" value for dissolved $\text{N}_2\text{O}$. The median of the empirical 
measurements was used for values of $M_h$ and $M_r$ (M_a_n2o).
```{r dg_calc, echo=TRUE}
# Set volume of syringe/vessel
V <- 140 # 140mL syringe

@@

B <- 99 # barometric pressure (kPa)
V_g <- V * R_M # volume of reference gas in headspace
V_w <- V * (1 - R_M) # volume of water below headspace
T_c <- 23 # temperature ( C )
M_h <- 0.307 # gas measured in headspace; Changes as function of R_M at constant C
M_a_n2o <- 0.310 # gas measured in reference (air)
H_n2o <- 0.00024 #mol m-3 Pa, range: 0.00018 - 0.00025; Henry's law constant
H_ar <- 0.000014 #mol m-3 Pa, range: 0.000013 - 0.000016; Henry's law constant

C <- 1e-6 * B * (V_g * (M_h - M_a_n2o) / (8.3144598 * (T_c + 273.15) * V_w) + H_n2o * exp(2700 * (1 / (T_c + 273.15) - 1 / 298.15)) * M_h)

@@

round(C, 1)

#### Re-arrange for Mh
M_h <- (((C / 1e9) * 8.3144598 * (T_c + 273.15) * V_w) + (1e-6 * B * V_g * M_a_n2o)) / (1e-6 * B * (V_g + 8.3144598 * (T_c + 273.15) * V_w * H_n2o * exp(2700 * (1 / (T_c + 273.15) - 1 / 298.15))))

M_h
```

## Empricial variation
```{r get_gc_error, echo=FALSE}
# READ GC DATA----------------
##########################################################################
#       Code is commented out because collaborators may not have access  #
#       to the file paths. The calculated standard deviation is hard     #
#       coded below.
##########################################################################

@@

Measurement error for this analysis is assumed to be the standard deviation of 
repeated analyses of the analytical standards throughout the period of time that
the NLA2017 samples were analyzed, which was $\sigma$ = `r n2o_sd_epa`.

## Simulate measurment error
Below, potential errors in GC measurements for are simulated and assessed s
eparately for measurements of $\text{N}_2\text{O}$ in:

@@

Error is then simulated and assessed separately for measurements of:

@@

    (6) water volume

Finally, all sources of error (1, 2, 4, 5, and 6) were simulated
simultaneously and assessed as an estimate of the total variation in $\text{N}_2\text{O}$ 
measurements. The estimated absolute error was added to each of the empirical 
point measurements recorded in this study, which resulted in an estimate of 
uncertainty due to measurement error for each empirical observation. The errors 
were also carried through for estimates of the saturation ratio and a 
categorical "source" or "sink" status was assigned for each site. This status 
was assigned such that any observations where the central 95th percentile of the 
measurement plus simulated error included 1.0 were deemed to be of 
"undeterminded" status. The source/sink/undetermined status for each site was 
then mapped.

Set the number of simulations for estimating error:
```{r set_n_sims}
nsim <- 1e5
```

### Equilibrated headspace
Simulate measurement error in dissolved $\text{N}_2\text{O}$ due solely to 
variation in GC measurements of gas in the equlibrated headspace ($M_h$ above).
```{r simulate_C_h_me, echo=TRUE, message=FALSE}
# Create empty vector to fill below with simulated values for N2O observed with 
# error due to variation in the GC measurments of gas in the equilibrated 
# headspace. The subscript, "me", denotes an observed or measured value, which 
# is contrasted with the known value, C, set above.
C_h_me <- rep(NA, nsim)

# The true value for the concentration of equilibrated gas in the headspace, 
# M_h, was set above. This step simulates additive error in this measurement 
# that is centered over the true value. The observed concentration of
# equilibrated gas, M_h_me, is simulated as normally distributed variable, with a mean
# M_h, and a standard deviation specified as the observed sd of replicate GC 
# measurements in our lab. 
M_h_me <- rnorm(nsim, M_h, n2o_sd_epa)

@@

The results of the simulations are summarized using density histograms below.
```{r plot_C_h_me, echo=FALSE, fig.align='center', fig.asp=0.35, fig.width=8}
ggarrange(
ggplot(C_h_df, aes(x = M_h_me, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.001) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = M_h , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("Simulated variation in \nequilibrated headspace (Mh) \nGC measurement") +
  xlab("Concentration (nmol L-1)"),

@@

ggplot(C_h_df, aes(x = C_h_me_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle("Absolute error in dissolved \nN2O estimate (measured - true) \n") +
  xlab("Error (nMol)"),
nrow = 1
)
```

### Ambient air
Error in the GC measurements of $\text{N}_2\text{O}$ in the ambient air 
($M_r$ above) reference is simulated below. The result of the simulation is
plotted as a histogram to illustrate the variation in the measurement. The
resulting effect on the uncertainty in the simulated dissolved N2O observation 
is plotted along with the absolute error in the simulated measurement.
```{r simulate_me_Ca, message=F}
C_a_me <- rep(NA, nsim)

M_a_n2o_me <- rnorm(nsim, M_a_n2o, n2o_sd_epa) # m.e. measured gas in air

@@

ggplot(C_a_df, aes(x = C_a_me_abs, y = after_stat(density))) +  
  geom_histogram( binwidth = 0.01 ) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline( xintercept = 0 , color = 'red' ) +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle( "Absolute error in dissolved \nN2O estimate (measured - true) \n") +
  xlab( "Error (nMol)"),
nrow = 1)
```

### Water temperature
Next, error in water temperature measurements is simulated and its potential
effect on the final dissolved N2O concentration assessed.
```{r simulate_me_T_c, message=F}
C_tc_me <- rep(NA, nsim)

@@

ggplot(C_tc_df, aes(x = C_tc_me_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.001) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) + 
  ggtitle("Absolute error in dissolved \nN2O estimate (measured - true) \n") +
  xlab("Error (nMol)"),
nrow = 1)
```

### Barometric pressure
Next, error in barometric pressure measurements is simulated and its potential
effect on the final dissolved N2O concentration assessed.
```{r simulate_me_B, message=F}
C_b_me <- rep(NA, nsim)

@@

ggplot(C_b_df, aes(x = C_b_me_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.0001) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) + 
  ggtitle("Absolute error in dissolved \nN2O estimate (measured - true) \n") +
  xlab("Error (nMol)"),
nrow = 1)
```

### Water volume
Next, error in the volume of water (relative to volume of gas) in the sample 
vessel is simulated and its potential effect on the final dissolved N2O 
concentration assessed.
```{r simulate_me_V_w, message=F}
C_w_me <- rep(NA, nsim)

@@

ggplot(C_w_df, aes(x = C_w_me_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.00025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) + 
  ggtitle("Absolute error in dissolved \nN2O estimate (measured - true) \n") +
  xlab("Error (nMol)"),
nrow = 1)
```

### Mixing ratio
To check the effect of different mixing ratios, we re-arrange the equation to 
solve for $M_h$, given a known $C$ from above where $C =$ `r round(C, 1)`. For 
both ambient air and a pure gas (e.g., helium) as the headspace gas, we evaluate 
three scenarios for the mixing ratio, $R_M$. The $R_M$ value indicates the 
proportion of gas relative to water in the headspace mixture. In the simulations 
below, we set $R_M$ to be (1) very low ($R_{M(low)} = 0.1$), (2) at equal mixing 
proportions ($R_{M(equal)} = 0.5$), and (3) very high ($R_{M(high)} = 0.9$). For 
reference, in the simulations above, and in the empirical field measurments, 
$R_M$ was set at `r R_M`. Also note that the total volume of the mixing vessel 
in the field study was `r V`mL, so the volume of gas in the mixing vessel was 
intended to be $R_M \cdot V_g =$ `r V_g`mL and the volume of water was 
$R_M \cdot V_w =$ `r V_w`mL. Finally, note that varying the total volume of the 
mixing vessel has no consequence for $C$, only the ratio of gas to water.

#### Ambient air
For the same fixed concentration, $C =$ `r round(C, 1)`, using a low proportion 
of gas relative to water ($R_{M(low)} = 0.1$) in the equilibrated headspace 
results in a smaller value of $M_h$ relative to the simulations above with
$R_M =$ `r R_M`. This simulation assumes ambient air is used as the headspace
gas.
```{r dg_calc_vary_rm_low, echo=TRUE}
# Set volume of syringe/vessel
V <- 140 # 140mL syringe

# Set ratio of gas volume to water volume in the mixing vessel to something
# smaller than the scenario above
R_M_low <- 0.1

C <- C # known N2O concentration in sample from simulation above
B <- 99 # barometric pressure (kPa)
V_g_low <- V * R_M_low # volume of reference gas in headspace
V_w_low <- V * (1 - R_M_low) # volume of water below headspace
T_c <- 23 # temperature ( C )
M_a_n2o <- 0.310 # gas measured in reference (air)
H_n2o <- 0.00024 #mol m-3 Pa, range: 0.00018 - 0.00025; Henry's law constant

#### Re-arranged previous equation to solve for Mh (with low proportion of gas to water)
M_h_low <- (((C / 1e9) * 8.3144598 * (T_c + 273.15) * V_w_low) + (1e-6 * B * V_g_low * M_a_n2o)) / (1e-6 * B * (V_g_low + 8.3144598 * (T_c + 273.15) * V_w_low * H_n2o * exp(2700 * (1 / (T_c + 273.15) - 1 / 298.15))))

round(M_h_low, 3)
```

Next, we calculate $M_h$ for equal proportions of gas and water in 
the headspace, such that $R_{M(equal)} = 0.5$. In this case we get a slightly 
higher value for $M_h$ relative to the low mixing proportion above.
```{r dg_calc_vary_rm_equal, echo=TRUE}
# Set volume of syringe/vessel
V <- 140 # 140mL syringe

# Set ratio of gas volume to water volume in the mixing vessel to something
# smaller than the scenario above
R_M_equal <- 0.5

C <- C # known N2O concentration in sample from simulation above
B <- 99 # barometric pressure (kPa)
V_g_equal <- V * R_M_equal # volume of reference gas in headspace
V_w_equal <- V * (1 - R_M_equal) # volume of water below headspace
T_c <- 23 # temperature ( C )
M_a_n2o <- 0.310 # gas measured in reference (air)
H_n2o <- 0.00024 #mol m-3 Pa, range: 0.00018 - 0.00025; Henry's law constant

#### Re-arranged previous equation to solve for Mh
M_h_equal <- (((C / 1e9) * 8.3144598 * (T_c + 273.15) * V_w_equal) + (1e-6 * B * V_g_equal * M_a_n2o)) / (1e-6 * B * (V_g_equal + 8.3144598 * (T_c + 273.15) * V_w_equal * H_n2o * exp(2700 * (1 / (T_c + 273.15) - 1 / 298.15))))

round(M_h_equal, 3)
```

Next, we calculate $M_h$ for a higher proportion of gas relative to water in 
the headspace, such that $R_{M(high)} = 0.9$. In this case we again get a higher 
value for $M_h$.
```{r dg_calc_vary_rm_high, echo=TRUE}
# Set volume of syringe/vessel
V <- 140 # 140mL syringe

# Set ratio of gas volume to water volume in the mixing vessel to something
# smaller than the scenario above
R_M_high <- 0.9

C <- C # known N2O concentration in sample from simulation above
B <- 99 # barometric pressure (kPa)
V_g_high <- V * R_M_high # volume of reference gas in headspace
V_w_high <- V * (1 - R_M_high) # volume of water below headspace
T_c <- 23 # temperature ( C )
M_a_n2o <- 0.310 # gas measured in reference (air)
H_n2o <- 0.00024 #mol m-3 Pa, range: 0.00018 - 0.00025; Henry's law constant

#### Re-arranged previous equation to solve for Mh
M_h_high <- (((C / 1e9) * 8.3144598 * (T_c + 273.15) * V_w_high) + (1e-6 * B * V_g_high * M_a_n2o)) / (1e-6 * B * (V_g_high + 8.3144598 * (T_c + 273.15) * V_w_high * H_n2o * exp(2700 * (1 / (T_c + 273.15) - 1 / 298.15))))

round(M_h_high, 3)
```

Finally, we simulate $C$ again with measurment error on $M_h$, but using the
values of $M_h$ obtained above using the 3 different values of $R_M$.

##### $R_{M(low)}$
```{r simulate_C_h_me_low, echo=TRUE, message=FALSE}
C_h_me_low <- rep(NA, nsim)

M_h_me_low <- rnorm(nsim, M_h_low, n2o_sd_epa)

for(i in 1:nsim){
  C_h_me_low[i] <- 1e-6 * B * (V_g_low * (M_h_me_low[i] - M_a_n2o) / (8.3144598 * (T_c + 273.15) * V_w_low) + H_n2o * exp(2700 * (1 / (T_c + 273.15) - 1 / 298.15)) * M_h_me_low[i])
}

# combine into dataframe for ggplot. 
C_h_low_df <- tibble(C_h_me_low = C_h_me_low, M_h_me_low = M_h_me_low)
# save absolute error for plot
C_h_me_low_abs <- (C_h_me_low * 1e9) - C
```

```{r plot_C_h_me_low, echo=FALSE, fig.align='center', fig.asp=0.35, fig.width=8}
ggarrange(
ggplot(C_h_low_df, aes(x = M_h_me_low, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.001) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = M_h_low , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("Simulated variation in \nequilibrated headspace (Mh) \nGC measurement") +
  xlab("Concentration (nmol L-1)"),

ggplot(C_h_low_df, aes(x = C_h_me_low * 1e9, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = C , color = 'red') +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle("Resulting uncertainty in \ndissolved N2O estimate \n") +
  xlab("Concentration (nMol)"),

ggplot(C_h_low_df, aes(x = C_h_me_low_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle("Absolute error in dissolved \nN2O estimate (measured - true) \n") +
  xlab("Error (nMol)"),
nrow = 1
)
```

##### $R_{M(equal)}$
```{r simulate_C_h_me_equal, echo=TRUE, message=FALSE}
C_h_me_equal <- rep(NA, nsim)

M_h_me_equal <- rnorm(nsim, M_h_equal, n2o_sd_epa)

for(i in 1:nsim){
  C_h_me_equal[i] <- 1e-6 * B * (V_g_equal * (M_h_me_equal[i] - M_a_n2o) / (8.3144598 * (T_c + 273.15) * V_w_equal) + H_n2o * exp(2700 * (1 / (T_c + 273.15) - 1 / 298.15)) * M_h_me_equal[i])
}

# combine into dataframe for ggplot. 
C_h_equal_df <- tibble(C_h_me_equal = C_h_me_equal, M_h_me_equal = M_h_me_equal)
# save absolute error for plot
C_h_me_equal_abs <- (C_h_me_equal * 1e9) - C
```

```{r plot_C_h_me_equal, echo=FALSE, fig.align='center', fig.asp=0.35, fig.width=8}
ggarrange(
ggplot(C_h_equal_df, aes(x = M_h_me_equal, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.001) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = M_h_equal , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("Simulated variation in \nequilibrated headspace (Mh) \nGC measurement") +
  xlab("Concentration (nmol L-1)"),

ggplot(C_h_equal_df, aes(x = C_h_me_equal * 1e9, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = C , color = 'red') +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle("Resulting uncertainty in \ndissolved N2O estimate \n") +
  xlab("Concentration (nMol)"),

ggplot(C_h_equal_df, aes(x = C_h_me_equal_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle("Absolute error in dissolved \nN2O estimate (measured - true) \n") +
  xlab("Error (nMol)"),
nrow = 1
)
```

##### $R_{M(high)}$
```{r simulate_C_h_me_high, echo=TRUE, message=FALSE}
C_h_me_high <- rep(NA, nsim)

M_h_me_high <- rnorm(nsim, M_h_high, n2o_sd_epa)

for(i in 1:nsim){
  C_h_me_high[i] <- 1e-6 * B * (V_g_high * (M_h_me_high[i] - M_a_n2o) / (8.3144598 * (T_c + 273.15) * V_w_high) + H_n2o * exp(2700 * (1 / (T_c + 273.15) - 1 / 298.15)) * M_h_me_high[i])
}

# combine into dataframe for ggplot. 
C_h_high_df <- tibble(C_h_me_high = C_h_me_high, M_h_me_high = M_h_me_high)
# save absolute error for plot
C_h_me_high_abs <- (C_h_me_high * 1e9) - C
```

```{r plot_C_h_me_high, echo=FALSE, fig.align='center', fig.asp=0.35, fig.width=8}
ggarrange(
ggplot(C_h_high_df, aes(x = M_h_me_high, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.001) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = M_h_high , color = 'red') + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("Simulated variation in \nequilibrated headspace (Mh) \nGC measurement") +
  xlab("Concentration (nmol L-1)"),

ggplot(C_h_high_df, aes(x = C_h_me_high * 1e9, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = C , color = 'red') +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle("Resulting uncertainty in \ndissolved N2O estimate \n") +
  xlab("Concentration (nMol)"),

ggplot(C_h_high_df, aes(x = C_h_me_high_abs, y = after_stat(density))) +  
  geom_histogram(binwidth = 0.025) + 
  geom_density(aes(y = after_stat(density)), color = 'green') +
  geom_vline(xintercept = 0 , color = 'red') +  
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  ggtitle("Absolute error in dissolved \nN2O estimate (measured - true) \n") +
  xlab("Error (nMol)"),
nrow = 1
)
```

#### Pure gas
To check the effect of different mixing ratios using a pure gas such as helium 
as the headspace, we again re-arrange the equation to solve for $M_h$, given 
known $C$. In this case with a pure gas, we set $M_a = 0$.

For the same fixed concentration, $C$, using a low proportion of pure gas 
relative to water ($R_{M(low)} = 0.1$) in the equilibrated headspace results in 
a much smaller value of $M_h$ relative to the original simulations (and field 
method) where $R_M =$ `r R_M`. This is because the mixing ratio is very low and 
also because there is no need to account for ambient air in the headspace.
```{r dg_calc_vary_rm_pg_low, echo=TRUE}
# Set volume of syringe/vessel
V <- 140 # 140mL syringe

# Set ratio of gas volume to water volume in the mixing vessel to something
# smaller than the scenario above
R_M_low <- 0.1

C <- C # known N2O concentration in sample from simulation above
B <- 99 # barometric pressure (kPa)
V_g_low <- V * R_M_low # volume of reference gas in headspace
V_w_low <- V * (1 - R_M_low) # volume of water below headspace
T_c <- 23 # temperature ( C )
H_n2o <- 0.00024 #mol m-3 Pa, range: 0.00018 - 0.00025; Henry's law constant

#### Re-arranged previous equation to solve for Mh
M_h_pg_low <- (((C / 1e9) * 8.3144598 * (T_c + 273.15) * V_w_low) + (1e-6 * B * V_g_low * 0)) / (1e-6 * B * (V_g_low + 8.3144598 * (T_c + 273.15) * V_w_low * H_n2o * exp(2700 * (1 / (T_c + 273.15) - 1 / 298.15))))

round(M_h_pg_low, 3)
```

Next, we calculate $M_h$ for equal proportions of pure gas and water in 
the headspace, such that $R_{M(equal)} = 0.5$. In this case we get a 
substantially lower value for $M_h$ relative to the low mixing proportion above.
```{r dg_calc_vary_rm_pg_equal, echo=TRUE}
# Set volume of syringe/vessel
V <- 140 # 140mL syringe

# Set ratio of gas volume to water volume in the mixing vessel to something
# smaller than the scenario above
R_M_equal <- 0.5

C <- C # known N2O concentration in sample from simulation above
B <- 99 # barometric pressure (kPa)
V_g_equal <- V * R_M_equal # volume of reference gas in headspace
V_w_equal <- V * (1 - R_M_equal) # volume of water below headspace
T_c <- 23 # temperature ( C )
H_n2o <- 0.00024 #mol m-3 Pa, range: 0.00018 - 0.00025; Henry's law constant
